---
title: "PatientID: output_id"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: pdf_document
header-includes:
  - \usepackage{titling}
  - \pretitle{\begin{flushleft}}
  - \posttitle{\end{flushleft}}
  - \predate{\begin{flushleft}\large}
  - \postdate{\end{flushleft}}
warning: FALSE
---

```{r load-packages, echo=FALSE, warning=FALSE, message=FALSE, CACHE = TRUE}
library(dplyr)
library(knitr)
library(kableExtra)
library(tidyr)
```

```{r load-data, echo=FALSE, warning=FALSE, message=FALSE, results='hide', CACHE = TRUE}
res_drug <- read.csv("resistance profile", header = T)
drugs <- read.csv("~/HIV-DRIVES/databases/drug_names_rmd.csv")
comments <- read.csv("comments profile", sep = "\t", header = T)
```

## Color Code

\begin{minipage}{0.7\textwidth}
\raggedright
\textcolor{red}{\rule{0.3cm}{0.3cm}} HR: High-Level Resistance \quad
\textcolor{blue}{\rule{0.3cm}{0.3cm}} PLR: Potential Low-Level Resistance \quad
\textcolor{orange}{\rule{0.3cm}{0.3cm}} LR: Low-Level Resistance \quad
\textcolor{pink}{\rule{0.3cm}{0.3cm}} IR: Intermediate Resistance \\
\textcolor{green}{\rule{0.3cm}{0.3cm}} S: Susceptible \quad
\end{minipage}

```{r process, echo=FALSE, warning=FALSE, message=FALSE, CACHE = TRUE}
res_drug_col <- res_drug %>%
  mutate(RESISTANCE.PROFILE = cell_spec(RESISTANCE.PROFILE, background = ifelse(RESISTANCE.PROFILE == "S", "green",
                                                                                ifelse(RESISTANCE.PROFILE == "PLR", "blue",
                                                                                       ifelse(RESISTANCE.PROFILE == "LR", "orange",
                                                                                              ifelse(RESISTANCE.PROFILE == "IR", "pink",
                                                                                                     ifelse(RESISTANCE.PROFILE == "HR", "red", "purple"))))), bold = T))
res_drug_col <- res_drug_col %>% mutate_all(~ifelse(is.na(.), "", as.character(.)))
# 
kable(res_drug_col, escape = F, align = "cccl", longtable = T) %>%
  kable_styling(latex_options = c("scale_down")) %>%
  kable_styling(latex_options = "HOLD_position") %>%
  row_spec(0, bold = T) %>%
  column_spec(1, bold = T) %>%
  column_spec(1, border_left = T) %>%
  column_spec(4, border_right = T) %>%
  collapse_rows(columns = c(1,4))
```

\newpage

# Appendix

## Drug abbreviations in full

```{r drugs, echo=FALSE, warning=FALSE, message=FALSE, CACHE = TRUE}
drugs <- drugs %>% mutate_all(~ifelse(is.na(.), "", as.character(.)))
kable(drugs, align = "ccc", longtable = T) %>% 
  kable_styling(latex_options = c("scale_down")) %>%
  kable_styling(latex_options = "HOLD_position") %>%
  row_spec(0, bold = T) %>%
  column_spec(1, bold = T) %>%
  column_spec(1, border_left = T) %>%
  column_spec(3, border_right = T) %>%
  collapse_rows(columns = 1)
```

## Comments

```{r comments, echo=FALSE, warning=FALSE, message=FALSE, CACHE = TRUE}
comments <- comments %>% mutate_all(~ifelse(is.na(.), "", as.character(.)))
kable(comments, align = "cl", longtable = T) %>% 
  kable_styling(latex_options = c("scale_down")) %>%
  kable_styling(latex_options = "HOLD_position") %>%
  row_spec(0, bold = T) %>%
  column_spec(1, bold = T) %>%
  column_spec(1, border_left = T) %>%
  column_spec(2, border_right = T) %>%
  column_spec(2, width = "40em") %>% 
  collapse_rows(columns = 1)
```
